---
title: "Reward Matrix"
author: "Min-Chun Shih"
output: 
  html_document:
    toc: true
    toc_float: TRUE
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(dplyr)
library(ggplot2)
library(knitr)
library(kableExtra)
library(gridExtra)
```

Only use data from season 2013-2014

```{r, eval = FALSE}
# import data
# ======= game type (regular season/playoffs) =======
game <- read.csv("../data/game.csv", sep = ";")
game$Season <- as.character(game$Season)
game <- game[which(game$Season == "2013-2014"), ]

# ======= goals records =======
state <- read.csv("../data/event_goal.csv", header = FALSE)
names(state) <- c(
  "GoalId",
  "GameId",
  "AwayTeamId",
  "HomeTeamId",
  "EventNumber",
  "PeriodNumber",
  "EventTime",
  "ScoringTeam",
  "ScoringTeamId",
  "Disposition",
  "GoalScorerNumber",
  "GoalScorerId",
  "NumGoals",
  "FirstAssistNumber",
  "FirstAssistId",
  "NumAssistsFirstPlayer",
  "SecondAssistNumber",
  "SecondAssistId",
  "NumAssistsSecondPlayer",
  "ShotType",
  "Zone",
  "ShotDistance")

# select the columns
state <- state[, c("GameId", "AwayTeamId", "HomeTeamId", "PeriodNumber", "EventTime", "ScoringTeamId")]

# merge state data and game data to get Season and SeasonType
state <- left_join(game, state)
state <- state[which(state$PeriodNumber %in% 1:3), ]

# ======= Manpower =======
events <- read.csv("../data/play_by_play_events.csv", sep = ";")

# merge with game data to get Season and SeasonType
events <- events[which(events$PeriodNumber %in% 1:3), ]
events <- left_join(game, events)


# compute manpower for away and home teams
for (i in 12:29) {
  events[, i] <- as.character(events[, i])
}
manpowewr <- unlist(lapply(1:nrow(events), function(x) {
  length(which(events[x, 12:20] != "NULL"))
}))
events$ManpowerAway <- manpowewr

manpowewr <- unlist(lapply(1:nrow(events), function(x) {
  length(which(events[x, 21:29] != "NULL"))
}))
events$ManpowerHome <- manpowewr

save(events, file = "../data/events.rdata")

manpower <- events[, c("GameId", "PeriodNumber", "EventTime", "ManpowerAway", "ManpowerHome")]
manpower <- unique(manpower)
save(manpower, file = "../data/manpower.Rdata")

# filter GOAL events
events <- events[which(events$EventType =="GOAL"), ]
events <- events[, c("GameId", "PeriodNumber", "EventTime", "ManpowerAway", "ManpowerHome")]

state$EventTime <- as.character(state$EventTime)
events$EventTime <- as.character(events$EventTime)



df <- inner_join(state, events)

df$EventTime <- as.character(df$EventTime)
df$seconds <- as.integer(substr(df$EventTime, 4, 5))*60 + 
  as.integer(substr(df$EventTime, 7, 8))

save(df, file = "../data/seaon20132014.rdata")
```



```{r}
load("../data/seaon20132014.rdata")
```


# Number of games
```{r}
unique_game <- unique(df[, c("GameId", "SeasonType")])
kable(table(unique_game$SeasonType), caption = "The amount of Games") %>%
  kable_styling(bootstrap_options = "striped", full_width = F, 
                position = "left")
```

# Distribution of goals in different period time
```{r}
i <- which(df$PeriodNumber == 1)
ii <- intersect(which(df$SeasonType == "Regular Season"), i)
plot1 <- ggplot(df[ii, ], aes(x = seconds)) + 
  geom_histogram(color="black", fill="gold1", alpha=0.7) +
  theme_bw() +
  labs(title = "The distibution of Goals in Times (Regular Season)",
       subtitle="PeriodNumber is 1") +
  geom_hline(aes(yintercept=
                   mean(table(cut(df[ii, "seconds"],
                                  breaks = 30)))),
             color="red", linetype="dashed", size=0.5)
jj <- intersect(which(df$SeasonType == "Playoffs"), i)
plot2 <- ggplot(df[jj, ], aes(x = seconds)) + 
  geom_histogram(color="black", fill="gold1", alpha=0.7) +
  theme_bw() +
  labs(title = "The distibution of Goals in Times (Playoffs)",
       subtitle="PeriodNumber is 1") +
  geom_hline(aes(yintercept=
                   mean(table(cut(df[jj, "seconds"],
                                  breaks = 30)))),
             color="red", linetype="dashed", size=0.5)
grid.arrange(plot1, plot2)

i <- which(df$PeriodNumber %in% c(2) == TRUE)
ii <- intersect(which(df$SeasonType == "Regular Season"), i)
plot1 <- ggplot(df[ii, ], aes(x = seconds)) + 
  geom_histogram(color="black", fill="gold1", alpha=0.7) +
  theme_bw() +
  labs(title = "The distibution of Goals in Times (Regular Season)",
       subtitle="PeriodNumber is 2") +
  geom_hline(aes(yintercept=
                   mean(table(cut(df[ii, "seconds"],
                                  breaks = 30)))),
             color="red", linetype="dashed", size=0.5)
jj <- intersect(which(df$SeasonType == "Playoffs"), i)
plot2 <- ggplot(df[jj, ], aes(x = seconds)) + 
  geom_histogram(color="black", fill="gold1", alpha=0.7) +
  theme_bw() +
  labs(title = "The distibution of Goals in Times (Playoffs)",
       subtitle="PeriodNumber is 2") +
  geom_hline(aes(yintercept=
                   mean(table(cut(df[jj, "seconds"],
                                  breaks = 30)))),
             color="red", linetype="dashed", size=0.5)
grid.arrange(plot1, plot2)

i <- which(df$PeriodNumber %in% c(3) == TRUE)
ii <- intersect(which(df$SeasonType == "Regular Season"), i)
plot1 <- ggplot(df[ii, ], aes(x = seconds)) + 
  geom_histogram(color="black", fill="gold1", alpha=0.7) +
  theme_bw() +
  labs(title = "The distibution of Goals in Times (Regular Season)",
       subtitle="PeriodNumber is 3") +
  geom_hline(aes(yintercept=
                   mean(table(cut(df[ii, "seconds"],
                                  breaks = 30)))),
             color="red", linetype="dashed", size=0.5)
jj <- intersect(which(df$SeasonType == "Playoffs"), i)
plot2 <- ggplot(df[jj, ], aes(x = seconds)) + 
  geom_histogram(color="black", fill="gold1", alpha=0.7) +
  theme_bw() +
  labs(title = "The distibution of Goals in Times (Playoffs)",
       subtitle="PeriodNumber is 3") +
  geom_hline(aes(yintercept=
                   mean(table(cut(df[jj, "seconds"],
                                  breaks = 30)))),
             color="red", linetype="dashed", size=0.5)
grid.arrange(plot1, plot2)

library(data.table)
df <- data.table(df)
```
```{r}
rm(plot1, plot2, i, ii, jj)
```

```{r, eval = FALSE}
library(tidyr)

# ======= game type (regular season/playoffs) =======
game <- read.csv("../data/game.csv", sep = ";")
game$Season <- as.character(game$Season)
game <- game[which(game$Season == "2013-2014"), ]

# ======= goals records =======
state <- read.csv("../data/event_goal.csv", header = FALSE)
names(state) <- c(
  "GoalId",
  "GameId",
  "AwayTeamId",
  "HomeTeamId",
  "EventNumber",
  "PeriodNumber",
  "EventTime",
  "ScoringTeam",
  "ScoringTeamId",
  "Disposition",
  "GoalScorerNumber",
  "GoalScorerId",
  "NumGoals",
  "FirstAssistNumber",
  "FirstAssistId",
  "NumAssistsFirstPlayer",
  "SecondAssistNumber",
  "SecondAssistId",
  "NumAssistsSecondPlayer",
  "ShotType",
  "Zone",
  "ShotDistance")

# select the columns
state <- state[, c("GameId", "AwayTeamId", "HomeTeamId", "PeriodNumber", "EventTime", "ScoringTeamId")]

# merge state data and game data to get Season and SeasonType
state <- left_join(game, state)


winer <- state %>% 
  group_by(GameId, ScoringTeamId) %>%
  summarise(goals = n())

# compute the goals of AwayTeam and HomeTeam for each game
goals_end <- distinct(state %>%
  select(GameId, AwayTeamId, HomeTeamId))

goals_end$AwayGoals <- 0
goals_end$HomeGoals <- 0

for (i in 1:nrow(goals_end)) {
  id <- goals_end$GameId[i]
  j <- which(winer$GameId == id)
  for (jj in j) {
    if(winer[jj, ]$ScoringTeamId == goals_end$AwayTeamId[i]) {
      goals_end$AwayGoals[i] <- winer[jj, ]$goals
    } else {
      goals_end$HomeGoals[i] <- winer[jj, ]$goals
    }
  }
}


winer <- winer %>%
  group_by(GameId) %>%
  filter(goals == max(goals)) %>%
  select(GameId, ScoringTeamId)
names(winer)[2] <- "Winer"

goals_end <- full_join(goals_end, winer)
save(goals_end, file = "../data/goals_end.Rdata")
```

```{r, eval = FALSE}
load("../data/goals_end.Rdata")
```

```{r, eval = FALSE}
### Compute seconds ###
# compute seconds 將時間換算成秒
df$seconds <- (df$PeriodNumber - 1)*20*60 + df$seconds
# order by seconds 根據節數與時間秒數排序
df <- df[order(df$GameId, df$seconds), ]

### compute GA&GF for period 1-3 ###
# get away team goals
df$AwayTeamGoals <- ifelse(df$ScoringTeamId == df$AwayTeamId, 1, 0)
# get home team goals
df$HomeTeamGoals <- ifelse(df$ScoringTeamId == df$HomeTeamId, 1, 0)
# compute cumulate goals
df <- data.table(df)
GF <- df[, list(GF = cumsum(HomeTeamGoals)), by=list(GameId)]
GA <- df[, list(GA = cumsum(AwayTeamGoals)), by=list(GameId)]
df <- cbind(df, GF[, -1])
df <- cbind(df, GA[, -1])
# df <- data.frame(df)
df <- df[, c(-12, -13)]

df <- left_join(df, goals_end)

result_after_3_period <- df %>% 
  group_by(GameId) %>%
  filter(seconds == max(seconds)) %>%
  select(GameId, GF, GA)

result_after_3_period$result <- ifelse(result_after_3_period$GF == result_after_3_period$GA,
                                       "tied", "")
result_after_3_period <- result_after_3_period %>% select(GameId, result)

df$HomeResult <- ifelse(df$HomeTeamId == df$Winer, "win", "lose")

df <- left_join(df, result_after_3_period)
df$HomeResult <- ifelse(df$result == "", df$HomeResult, paste0(df$result, "_", df$HomeResult))
df$result <- NULL

save(df, file = "../data/df.Rdata")
```

```{r}
# the goal table
load(file = "../data/df.Rdata")
```


```{r}
# manpower for every events, it will be used for compute time interval's manpower
load("../data/manpower.Rdata")
manpower <- manpower[-which(manpower$ManpowerAway == 0 | manpower$ManpowerHome == 0), ]
manpower <- manpower[-which(manpower$ManpowerAway >= 7 | manpower$ManpowerHome >= 7), ]
manpower$seconds <- as.integer(substr(manpower$EventTime, 4, 5))*60 + 
  as.integer(substr(manpower$EventTime, 7, 8))
manpower$seconds <- (manpower$PeriodNumber - 1)*20*60 + manpower$seconds
manpower <- manpower[, c("GameId", "ManpowerAway", "ManpowerHome", "seconds")]
manpower$n <- 1:nrow(manpower)
manpower <- manpower %>%
  group_by(GameId, seconds) %>%
  filter(n == max(n))
manpower$n <- NULL
```

***

# Questions:

1. penalty in games?

```{r, eval = FALSE}
load("../data/events.rdata")
head(events[which(events$GameId == "2013020735"), ], 30)
head(events[which(events$GameId == "2013020735" & events$EventType == "PENALTY"), ], 50)

# SELECT * FROM `event_penalty` WHERE GameId = "2013020735"
# events[which(events$GameId == "2013020175"), ]
```

2. the manpower of the begining of games in period 2 and 3 is 0?
```{r, eval = FALSE}
events[which(events$GameId == "2013020175" & events$EventType == "PERIOD START"), c(1:11, 30, 31)]
head(events[which(events$EventType == "PERIOD START"), c(1:11, 30, 31)], 10)
```


```{r, eval=FALSE}
# get the conut matrix
get_count_matrix <- function(df, time_interval, type = c("ratio", "after")) {
  # compute interval
  interval <- cut(df$seconds, seq(0, 20*60*3, time_interval))
  
  df$interval <- interval
  df$index <- as.integer(df$interval)
  if (type == "ratio") {
    df$ratio <- (time_interval*df$index - df$seconds)/time_interval
  }
  if (type == "after") {
    df$ratio <- 1
  }
  
  # get the coount for every time interval for each game
  count <- data.table(GameId = as.character(), SeasonType = as.character(), interval = as.character(),
                   GF = as.integer(), GA = as.integer(), count = as.numeric(), 
                   ManpowerAway = as.integer(), ManpowerHome = as.integer(),
                   AwayGoals = as.integer(), HomeGoals = as.integer(), HomeResult = as.character())
  
  interval_levels <- factor(levels(interval), levels = levels(interval))
  n_interval <- length(levels(interval))
  
  # select the columns we need 
  d <- df %>%
    select(GameId, SeasonType, interval, GF, GA, count = ratio,
           ManpowerAway, ManpowerHome, AwayGoals, HomeGoals, HomeResult)
  
  if (type == "after") {
    d <- cbind(d, n = 1:nrow(d))
    d <- d %>% 
      group_by(GameId, count, interval) %>%
      filter(n == max(n))
    d$n <- NULL  
  }
  
  ids <- unique(d$GameId)
  
  for (id in ids) {
    # manpower for a game in each event(from play_by_play table)
    game_manpower <- manpower[which(manpower$GameId == id), ]
    
    t <- d[which(d$GameId == id), ] # the same game in d
    n <- nrow(t) # the number of goals in this game
    first <- as.integer(t$interval)[1] # the time interval index of first goal in this game
    freq <- data.frame(table(t$interval)) # the number of goals in each time interval
    AwayGoals <- t$AwayGoals[1]
    HomeGoals <- t$HomeGoals[1]
    HomeResult <- t$HomeResult[1]
    SeasonType <- as.character(t$SeasonType[1])
  
    # the time intervals which don't made any goal 先處理沒有得分的區間
    # all of the counts are 1 if there's no goal is made
    freq_0_interval <- which(freq$Freq == 0)
    for (i in freq_0_interval) {
      # manpower numbers are same as the last event
      nn <- which((game_manpower$seconds < as.integer(interval_levels[i])*time_interval)  == TRUE)
      manpower_row <- nn[length(nn)]
      manpower_away <- game_manpower[manpower_row, "ManpowerAway"]
      manpower_home <- game_manpower[manpower_row, "ManpowerHome"]
      
      ## i is before goals are made, gf and ga are 0
      if (i < first) {
        l = list(t, data.table(GameId = id, SeasonType = SeasonType, 
                               interval = interval_levels[i],
                               GF = 0, GA = 0, count = 1.0,
                               ManpowerAway = manpower_away, 
                               ManpowerHome = manpower_home,
                               AwayGoals = AwayGoals, HomeGoals = HomeGoals, 
                               HomeResult = HomeResult))
        ## i is after goals are made
      } else {
        ii <- which(t$interval == interval_levels[i-1])
        ii <- ii[length(ii)]
        l <- list(t, data.table(GameId = id, SeasonType = SeasonType, 
                                interval = interval_levels[i],
                                GF = t[ii, ]$GF, GA = t[ii, ]$GA, count = 1.0, 
                                ManpowerAway = manpower_away, 
                                ManpowerHome = manpower_home,
                                AwayGoals = AwayGoals, HomeGoals = HomeGoals,
                                HomeResult = HomeResult))
      }
      t <- rbindlist(l)
    }
    
    if (type == "ratio") {
      last_interval_level <- ""
      for (i in 1:n) {
        # manpower numbers are same as the last event
        ii <- as.integer(t[i, ]$interval)
        nn <- which((game_manpower$seconds < ii*time_interval)  == TRUE)
        manpower_row <- nn[length(nn)]
        manpower_away <- game_manpower[manpower_row, "ManpowerAway"]
        manpower_home <- game_manpower[manpower_row, "ManpowerHome"]
      
        if (last_interval_level != interval_levels[ii]) {
          if (i == 1) {
            # if it is the first time interval before made a goal, gf and ga are 0
            l <- list(t, data.table(GameId = id, SeasonType = SeasonType, 
                                    interval = interval_levels[ii],
                                    GF = 0, GA = 0, count = 1 - t[1, ]$count, 
                                    ManpowerAway = manpower_away, 
                                    ManpowerHome = manpower_home,
                                    AwayGoals = AwayGoals, HomeGoals = HomeGoals,
                                    HomeResult = HomeResult))
          } else {
            l <- list(t, data.table(GameId = id, SeasonType = SeasonType, 
                                    interval = interval_levels[ii],
                                    GF = t[i-1, ]$GF, GA = t[i-1, ]$GA,
                                    count = 1 - t[i, ]$count, 
                                    ManpowerAway = manpower_away, 
                                    ManpowerHome = manpower_home,
                                    AwayGoals = AwayGoals, HomeGoals = HomeGoals,
                                    HomeResult = HomeResult))
          }
        } else {
          jj <- which(t$interval == last_interval_level)
          l <- list(t, data.table(GameId = id, SeasonType = SeasonType, 
                                  interval = interval_levels[ii],
                                  GF = t[i-1, ]$GF, GA = t[i-1, ]$GA,
                                  count = 1 - sum(t[jj, ]$count), 
                                  ManpowerAway = manpower_away, 
                                  ManpowerHome = manpower_home,
                                  AwayGoals = AwayGoals, HomeGoals = HomeGoals,
                                  HomeResult = HomeResult))
        }
        t <- rbindlist(l)
        last_interval_level <- interval_levels[ii]
      }
    }
    
    # order rows by interval, gf and ga
    t <- t[order(t$interval, t$GF, t$GA), ]
    # combine all the count together
    l <- list(count, t)
    count <- rbindlist(l)
  }
  
  # group by (interval, GF, GA, ManpowerAway, ManpowerHome, AwayGoals, HomeGoals) to compute "count"
  count_matrix <- count %>%
    group_by(interval, SeasonType, GF, GA,
             ManpowerAway, ManpowerHome, AwayGoals, HomeGoals, HomeResult) %>%
    summarise(count = sum(count))
  
  # add manpower difference column
  count_matrix$ManpowerDiff <- count_matrix$ManpowerHome - count_matrix$ManpowerAway
  # add goal difference column
  # goals for:進球數，goals against:失球數
  count_matrix$GoalDiff <- count_matrix$GF - count_matrix$GA
  
  # add begin time and end time columns
  split_time <- strsplit(as.character(count_matrix$interval), ",")#[[1]]
  count_matrix$Begin <- sapply(split_time, function(x) {
    as.integer(substr(x[1], 2, nchar(x[1])))
  })
  count_matrix$End <- sapply(split_time, function(x) {
    as.integer(substr(x[2], 1, nchar(x[2]) -1))
  })
  
  # add Period column
  count_matrix$Period <- ifelse(count_matrix$End <= 1200, "1", 
                                ifelse(count_matrix$End <= 2400, "2", "3"))
  
  return(count_matrix)
}
```

***

```{r}
goal_diff <- unique(df[, c("GameId", "AwayGoals", "HomeGoals")])
final_goal_diff <- data.frame(table(goal_diff$HomeGoals - goal_diff$AwayGoals))
final_goal_diff$Var1 <- as.character(final_goal_diff$Var1)
plot(final_goal_diff$Var1, final_goal_diff$Freq, pch = 16, xlim = c(-8, 8), xaxt="n",
     main = "Distibution of final goal difference", xlab = "Goals", ylab = "Number")
lines(final_goal_diff$Var1, final_goal_diff$Freq)
axis(1, at=-8:8, labels=-8:8, las=1)

result <- unique(df[, c("GameId", "HomeResult")])
table(result$HomeResult)
```

***

# ===== Count Matrix - Ratio =====
```{r}
# function
goal_ditribution_plot <- function(df, time_interval) {
  d <- data.frame(table(cut(df$seconds, seq(0, 20*60*3, time_interval))))
  d$seq <- 1:nrow(d)
  d$Var1 <- as.character(d$Var1)
  par(mgp = c(0, 0.3, 0))
  barplot(d$Freq, main = paste("The goal distribution of time interval =", time_interval, "seconds"))
  title(xlab="Time interval", ylab="Number of goals", line=2, cex.lab=1.2)
}

count_group_homeresult <- function(count_matrix, time_interval, groupby = c("goaldiff", "manpowerdiff")) {
  if (groupby == "manpowerdiff") {
    count <- count_matrix %>%
      group_by(interval, HomeResult, ManpowerDiff) %>%
      summarise(count = sum(count))
  }
  
  # group by interval, result and goal difference, then sum up counts
  if (groupby == "goaldiff") {
    count <- count_matrix %>%
      group_by(interval, HomeResult, GoalDiff) %>%
      summarise(count = sum(count))
  }
  # count$interval <- as.character(count$interval)

  # lose
  count_lose <- count[which(count$HomeResult == "lose"), ]

  # win
  count_win <- count[which(count$HomeResult == "win"), ]
  
  # tied win
  count_tied_lose <- count[which(count$HomeResult == "tied_lose"), ]
  
  # tied win
  count_tied_win <- count[which(count$HomeResult == "tied_win"), ]

  return(list(count = count, count_lose = count_lose, count_win = count_win,
              count_tied_lose = count_tied_lose, count_tied_win = count_tied_win))
}

count_plot <- function(count, groupby = c("GoalDiff", "ManpowerDiff"), diff, result) {
  # labes for x axis
  labs <- levels(count$interval)
  i <- seq(round(length(labs)/9, 0), length(labs), round(length(labs)/9, 0))
  labs <- labs[i]
  # filter goal diff 
  count <- count[which(count[, groupby] == diff), ]
  count$count <- count$count*100/sum(count$count)
  
  # plot
  par(mgp = c(0, 0.5, 0))
  plot(count$interval, count$count, xaxt="n", 
       main = paste0(result, ", ", groupby, " = ", diff))
  lines(count$interval, count$count)
  abline(v = 3600/(3*time_interval) + 0.5, col = "grey", lty=2)
  abline(v = 3600*2/(3*time_interval) + 0.5, col = "grey", lty=2)
  abline(h = mean(count$count), col = "red", lty=2)
  title(xlab="Time interval", ylab="Sum of count (%)", line=2, cex.lab=1.2)
  text(x=i, y=min(count$count) - (max(count$count)- min(count$count))/10,
       labels=labs, xpd=TRUE, srt=30, cex=0.5)
}

all_plots <- function(df, type = c("GoalDiff", "ManpowerDiff")) {
  if (type == "GoalDiff") {
    result <- "win"
    par(mfrow=c(1,2))
    count_plot(df$count_win, "GoalDiff", 1, result)
    count_plot(df$count_win, "GoalDiff", 2, result)

    result <- "lose"
    par(mfrow=c(1,2))
    count_plot(df$count_lose, "GoalDiff", -1, result)
    count_plot(df$count_lose, "GoalDiff", -2, result)

    result <- "tied_win"
    par(mfrow=c(1,2))
    count_plot(df$count_tied_win, "GoalDiff", 1, result)
    count_plot(df$count_tied_win, "GoalDiff", 2, result)

    result <- "tied_lose"
    par(mfrow=c(1,2))
    count_plot(df$count_tied_lose, "GoalDiff", -1, result)
    count_plot(df$count_tied_lose, "GoalDiff", -2, result)
  }
  if (type == "ManpowerDiff") {
    result <- "win"
    count_plot(df$count_win, "ManpowerDiff", 0, result)

    par(mfrow=c(1,2))
    count_plot(df$count_win, "ManpowerDiff", 1, result)
    count_plot(df$count_win, "ManpowerDiff", 2, result)
    par(mfrow=c(1,2))
    count_plot(df$count_win, "ManpowerDiff", -1, result)
    count_plot(df$count_win, "ManpowerDiff", -2, result)

    result <- "lose"
    par(mfrow=c(1,1))
    count_plot(df$count_lose, "ManpowerDiff", 0, result)

    par(mfrow=c(1,2))
    count_plot(df$count_lose, "ManpowerDiff", 1, result)
    count_plot(df$count_lose, "ManpowerDiff", 2, result)
    par(mfrow=c(1,2))
    count_plot(df$count_lose, "ManpowerDiff", -1, result)
    count_plot(df$count_lose, "ManpowerDiff", -2, result)

    result <- "tied_win"
    par(mfrow=c(1,1))
    count_plot(df$count_tied_win, "ManpowerDiff", 0, result)

    par(mfrow=c(1,2))
    count_plot(df$count_tied_win, "ManpowerDiff", 1, result)
    count_plot(df$count_tied_win, "ManpowerDiff", 2, result)
    par(mfrow=c(1,2))
    count_plot(df$count_tied_win, "ManpowerDiff", -1, result)
    count_plot(df$count_tied_win, "ManpowerDiff", -2, result)

    result <- "tied_lose"
    par(mfrow=c(1,1))
    count_plot(df$count_tied_lose, "ManpowerDiff", 0, result)
    par(mfrow=c(1,2))
    count_plot(df$count_tied_lose, "ManpowerDiff", 1, result)
    count_plot(df$count_tied_lose, "ManpowerDiff", 2, result)
    par(mfrow=c(1,2))
    count_plot(df$count_tied_lose, "ManpowerDiff", -1, result)
    count_plot(df$count_tied_lose, "ManpowerDiff", -2, result)
  }
}
```

# Group by Home Team Result(win/lose/tied win/tied lose) & GoalDiff
## Time interval = 120 seconds

```{r}
time_interval <- 120
goal_ditribution_plot(df, time_interval)

# count_matrix_120 <- get_count_matrix(df, time_interval, type = "ratio")
# save(count_matrix_120, file = "../data/count_matrix_120.Rdata")
load("../data/count_matrix_120.Rdata")

count_120 <- count_group_homeresult(count_matrix_120, time_interval, groupby = "goaldiff")
# all_plots(count_120, type = "GoalDiff")
```

***

### Hometeam wins 
```{r}
result <- "win"
par(mfrow=c(1,1))
count_plot(count_120$count_win, "GoalDiff", 0, result)

par(mfrow=c(1,2))
count_plot(count_120$count_win, "GoalDiff", 1, result)
count_plot(count_120$count_win, "GoalDiff", 2, result)

# par(mfrow=c(1,2))
# count_plot(count_120$count_win, "GoalDiff", 3, result)
# count_plot(count_120$count_win, "GoalDiff", 4, result)

par(mfrow=c(1,2))
count_plot(count_120$count_win, "GoalDiff", -1, result)
count_plot(count_120$count_win, "GoalDiff", -2, result)
```

For GoalDiff = 0 plot, the value of count decreases from perid 1 to 3. In period 1, the trend goes down more significantly then in period 2 and 3, the value of count is below average after period 1. 

***

### Hometeam lose
```{r}
result <- "lose"
par(mfrow=c(1,1))
count_plot(count_120$count_lose, "GoalDiff", 0, result)

par(mfrow=c(1,2))
count_plot(count_120$count_lose, "GoalDiff", -1, result)
count_plot(count_120$count_lose, "GoalDiff", -2, result)

par(mfrow=c(1,2))
count_plot(count_120$count_lose, "GoalDiff", 1, result)
count_plot(count_120$count_lose, "GoalDiff", 2, result)
```

***

### Hometeam tied_win
```{r}
result <- "tied_win"
par(mfrow=c(1,1))
count_plot(count_120$count_tied_win, "GoalDiff", 0, result)

par(mfrow=c(1,2))
count_plot(count_120$count_tied_win, "GoalDiff", -1, result)
count_plot(count_120$count_tied_win, "GoalDiff", -2, result)

par(mfrow=c(1,2))
count_plot(count_120$count_tied_win, "GoalDiff", 1, result)
count_plot(count_120$count_tied_win, "GoalDiff", 2, result)
```

***

### Hometeam tied_lose
```{r}
result <- "tied_lose"
par(mfrow=c(1,1))
count_plot(count_120$count_tied_lose, "GoalDiff", 0, result)

par(mfrow=c(1,2))
count_plot(count_120$count_tied_lose, "GoalDiff", -1, result)
count_plot(count_120$count_tied_lose, "GoalDiff", -2, result)

par(mfrow=c(1,2))
count_plot(count_120$count_tied_lose, "GoalDiff", 1, result)
count_plot(count_120$count_tied_lose, "GoalDiff", 2, result)
```

***

```{r}
count_120_regular <- count_group_homeresult(count_matrix_120[which(count_matrix_120$SeasonType == "Regular Season"), ], time_interval, groupby = "goaldiff")
```

### Hometeam win(Regular season)

```{r}
result <- "win"
par(mfrow=c(1,1))
count_plot(count_120_regular$count_win, "GoalDiff", 0, result)

par(mfrow=c(1,2))
count_plot(count_120_regular$count_win, "GoalDiff", 1, result)
count_plot(count_120_regular$count_win, "GoalDiff", 2, result)

par(mfrow=c(1,2))
count_plot(count_120_regular$count_win, "GoalDiff", -1, result)
count_plot(count_120_regular$count_win, "GoalDiff", -2, result)
```

***

### Hometeam lose(Regular season)

```{r}
result <- "lose"
par(mfrow=c(1,1))
count_plot(count_120_regular$count_lose, "GoalDiff", 0, result)

par(mfrow=c(1,2))
count_plot(count_120_regular$count_lose, "GoalDiff", -1, result)
count_plot(count_120_regular$count_lose, "GoalDiff", -2, result)

par(mfrow=c(1,2))
count_plot(count_120_regular$count_lose, "GoalDiff", 1, result)
count_plot(count_120_regular$count_lose, "GoalDiff", 2, result)
```

***

### Hometeam tied_win(Regular season)

```{r}
result <- "tied_win"
par(mfrow=c(1,1))
count_plot(count_120_regular$count_tied_win, "GoalDiff", 0, result)

par(mfrow=c(1,2))
count_plot(count_120_regular$count_tied_win, "GoalDiff", 1, result)
count_plot(count_120_regular$count_tied_win, "GoalDiff", 2, result)

par(mfrow=c(1,2))
count_plot(count_120_regular$count_tied_win, "GoalDiff", -1, result)
count_plot(count_120_regular$count_tied_win, "GoalDiff", -2, result)
```

***

### Hometeam tied_lose(Regular season)

```{r}
result <- "tied_lose"
par(mfrow=c(1,1))
count_plot(count_120_regular$count_tied_lose, "GoalDiff", 0, result)

par(mfrow=c(1,2))
count_plot(count_120_regular$count_tied_lose, "GoalDiff", -1, result)
count_plot(count_120_regular$count_tied_lose, "GoalDiff", -2, result)

par(mfrow=c(1,2))
count_plot(count_120_regular$count_tied_lose, "GoalDiff", 1, result)
count_plot(count_120_regular$count_tied_lose, "GoalDiff", 2, result)
```

***

```{r}
count_120_playoffs <- count_group_homeresult(count_matrix_120[which(count_matrix_120$SeasonType == "Playoffs"), ], time_interval, groupby = "goaldiff")
```

### Hometeam win(Playoffs)

```{r}
result <- "win"
par(mfrow=c(1,1))
count_plot(count_120_playoffs$count_win, "GoalDiff", 0, result)

par(mfrow=c(1,2))
count_plot(count_120_playoffs$count_win, "GoalDiff", 1, result)
count_plot(count_120_playoffs$count_win, "GoalDiff", 2, result)

par(mfrow=c(1,2))
count_plot(count_120_playoffs$count_win, "GoalDiff", -1, result)
count_plot(count_120_playoffs$count_win, "GoalDiff", -2, result)
```

***

### Hometeam lose(Playoffs)

```{r}
result <- "lose"
par(mfrow=c(1,1))
count_plot(count_120_playoffs$count_lose, "GoalDiff", 0, result)

par(mfrow=c(1,2))
count_plot(count_120_playoffs$count_lose, "GoalDiff", -1, result)
count_plot(count_120_playoffs$count_lose, "GoalDiff", -2, result)

par(mfrow=c(1,2))
count_plot(count_120_playoffs$count_lose, "GoalDiff", 1, result)
count_plot(count_120_playoffs$count_lose, "GoalDiff", 2, result)
```

***

### Hometeam tied_win(Playoffs)

```{r}
result <- "tied_win"
par(mfrow=c(1,1))
count_plot(count_120_playoffs$count_tied_win, "GoalDiff", 0, result)

par(mfrow=c(1,2))
count_plot(count_120_playoffs$count_tied_win, "GoalDiff", 1, result)
count_plot(count_120_playoffs$count_tied_win, "GoalDiff", 2, result)

par(mfrow=c(1,2))
count_plot(count_120_playoffs$count_tied_win, "GoalDiff", -1, result)
count_plot(count_120_playoffs$count_tied_win, "GoalDiff", -2, result)
```

***

### Hometeam tied_lose(Playoffs)

```{r}
result <- "tied_lose"
par(mfrow=c(1,1))
count_plot(count_120_playoffs$count_tied_lose, "GoalDiff", 0, result)

par(mfrow=c(1,2))
count_plot(count_120_playoffs$count_tied_lose, "GoalDiff", -1, result)
count_plot(count_120_playoffs$count_tied_lose, "GoalDiff", -2, result)

par(mfrow=c(1,2))
count_plot(count_120_playoffs$count_tied_lose, "GoalDiff", 1, result)
count_plot(count_120_playoffs$count_tied_lose, "GoalDiff", 2, result)
```

***

## Time interval = 60 seconds
```{r, eval = FALSE}
time_interval <- 60
goal_ditribution_plot(df, time_interval)

# count_matrix_60 <- get_count_matrix(df, time_interval, type = "ratio")
# save(count_matrix_60, file = "../data/count_matrix_60.Rdata")
load("../data/count_matrix_60.Rdata")
count_60 <- count_group_homeresult(count_matrix_60, time_interval, groupby = "goaldiff")
all_plots(count_60, type = "GoalDiff")
```

## Time interval = 30 seconds
```{r, eval = FALSE}
time_interval <- 30
goal_ditribution_plot(df, time_interval)

# count_matrix_30 <- get_count_matrix(df, time_interval, type = "ratio")
# save(count_matrix_30, file = "../data/count_matrix_30.Rdata")
load("../data/count_matrix_30.Rdata")
count_30 <- count_group_homeresult(count_matrix_30, time_interval, groupby = "goaldiff")
all_plots(count_30, type = "GoalDiff")
```

# Group by Home Team Result(win/lose/tied win/tied lose) & ManpowerDiff
## Time interval = 120 seconds
```{r}
time_interval <- 120
count_120 <- count_group_homeresult(count_matrix_120, time_interval, groupby = "manpowerdiff")
all_plots(count_120, type = "ManpowerDiff")
```

## Time interval = 60 seconds
```{r, eval = FALSE}
time_interval <- 60
count_60 <- count_group_homeresult(count_matrix_60, time_interval, groupby = "manpowerdiff")
all_plots(count_60, type = "ManpowerDiff")
```

## Time interval = 30 seconds
```{r, eval = FALSE}
time_interval <- 30
count_30 <- count_group_homeresult(count_matrix_30, time_interval, groupby = "manpowerdiff")
all_plots(count_30, type = "ManpowerDiff")
```

# ===== Count Matrix - After =====
# Group by Home Team Result(win/lose/tied win/tied lose) & GoalDiff
## Time interval = 120 seconds
```{r}
time_interval <- 120
# count_matrix_120_after <- get_count_matrix(df, time_interval, type = "after")
# save(count_matrix_120_after, file = "../data/count_matrix_120_after.Rdata")
load("../data/count_matrix_120_after.Rdata")
count_120 <- count_group_homeresult(count_matrix_120_after, time_interval, groupby = "goaldiff")
all_plots(count_120, type = "GoalDiff")
```

## Time interval = 60 seconds
```{r, eval = FALSE}
time_interval <- 60
# count_matrix_60_after <- get_count_matrix(df, time_interval, type = "after")
# save(count_matrix_60_after, file = "../data/count_matrix_60_after.Rdata")
load("../data/count_matrix_60_after.Rdata")
count_60 <- count_group_homeresult(count_matrix_60_after, time_interval, groupby = "goaldiff")
all_plots(count_60, type = "GoalDiff")
```

## Time interval = 30 seconds
```{r, eval = FALSE}
time_interval <- 30
# count_matrix_30_after <- get_count_matrix(df, time_interval, type = "after")
# save(count_matrix_30_after, file = "../data/count_matrix_30_after.Rdata")
load("../data/count_matrix_30_after.Rdata")
count_30 <- count_group_homeresult(count_matrix_30_after, time_interval, groupby = "goaldiff")
all_plots(count_30, type = "GoalDiff")
```

***

# Group by Home Team Result(win/lose/tied win/tied lose) & ManpowerDiff
## Time interval = 120 seconds
```{r}
time_interval <- 120
count_120 <- count_group_homeresult(count_matrix_120_after, time_interval, groupby = "manpowerdiff")
all_plots(count_120, type = "ManpowerDiff")
```

## Time interval = 60 seconds
```{r, eval = FALSE}
time_interval <- 60
count_60 <- count_group_homeresult(count_matrix_60_after, time_interval, groupby = "manpowerdiff")
all_plots(count_60, type = "ManpowerDiff")
```

## Time interval = 30 seconds
```{r, eval = FALSE}
time_interval <- 30
count_30 <- count_group_homeresult(count_matrix_30_after, time_interval, groupby = "manpowerdiff")
all_plots(count_30, type = "ManpowerDiff")
```

***
# ==============================


# Analysis

1. Different intervals - The trend of lines are almost same for different intervals, but smaller intervals give more details about the ups-and-downs of the count value. 

2. Different counting method - It doesn't have very significant difference of fluctuation between ratio method and after method, the main trend for each plot is quite similar. 

3. Regular Season vs Playoffs - The plots of count values for Regular Season games are basically looks same as the plots for Regular Season + Playoffs games. For Playoffs games, although the data for Playoffs games are not that enough, but still can see the roughly trends. It approximatly flucduate similar as Regular Season.






